---
title: "Generate categorical bed"
author: "Sara Lago"
date: "2025-04-14"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

####################################### GENERATE A CATEGORICAL BED FROM UCSC DATA ##############################################

The following script aims at merging sevaral information retrieved from UCSC Table Browser (hg38 specific) about regulatory elements.
These files have been downloaded as .bed format and contain:
- TSS peaks
- CpG Islands
- VISTA enhancers (https://enhancer.lbl.gov/vista/)

So, as a first step we will load these data:

```{r load bed data}
# Read files in to a unique list
setwd("C:/Users/sarlago/Documents/R scripts/hg38_regulatory_elements_UCSC")
files <- list.files(pattern = ".bed", full.names = T)
files.list <- lapply(files, read.table, header = F, sep = "\t")
# Rename list elements based on file names
names(files.list) <- gsub("./|.bed", "", files)
```

Once we have the list of all files in data.frame format we will generate a unique table that containes just the genomic positions (chr, start, end) and a 4th column with the category name:

```{r add cat name}
# Merge the data frames in the list by row and by selecting just the first three columns which corespond to V1 = chr, V2 = start, V3 = end
merged.cat.bed <- dplyr::bind_rows(lapply(files.list[], `[`, 1:3), .id = "category")
# Since with this function the category name will be the first column, we need to move it as last and rename the other three appropriately:
merged.cat.bed <- merged.cat.bed[,c(2,3,4,1)]
names(merged.cat.bed)[1:3] <- c("chr", "start", "end")
```

Finally we export the file:

```{r write file output}
write.table(x = merged.cat.bed, file = "regulatory_elements_hg38.bed", sep = "\t", quote = F, row.names = F, col.names = T)
```


```{r sessionInfo}
sessionInfo()
```

