---
title: "GWAS_data_organization_for_plotgardener"
author: "Sara Lago"
date: "2025-04-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load required libraries:
```{r libraries}
library(dplyr)

```


### SHORT TABLE SOLUTION
Use the script in the chunk below to generate a table with JUST the required columns, check that the column names of the input table match the required. They should have been uniformed due to recent rules for submission. Update the config file accordingly with the name of the output file.

```{r read GWAS}
# Read the complete table
man.data <- read.table("C:/Users/sarlago/Documents/R scripts/Shiny/ShinyTest/data/GWAScatalog_KidneyDisease/26831199-GCST003374-EFO_0003884.h.tsv.gz", sep = "\t", header = T) 

# remove NAs
man.data <-  man.data[!is.na(man.data$hm_chrom),]
# paste chr to chr name
man.data$hm_chrom <- paste("chr", man.data$hm_chrom, sep="")
# select just the columns with the required info and write output to file
man.data %>% 
  select("hm_chrom", "hm_pos", "p_value", "hm_rsid") %>% 
  write.table("C:/Users/sarlago/Documents/R scripts/Shiny/ShinyTest/data/GWAScatalog_KidneyDisease/26831199-GCST003374-EFO_0003884.h.selectedCol.tsv.gz", sep="\t", col.names = c("chrom", "pos", "p", "snp"), row.names = F, quote = F)

unique(man.data$hm_chrom)
```

### EXTENDED TABLE SOLUTION
Use the script in the chunk below to generate a table with the required columns plus additional OPTIONAL columns that might be present in the original dataset, check that the column names of the input table match the required. They should have been uniformed due to recent rules for submission. Update the config file accordingly with the name of the output file.


```{r read GWAS with ptional fields}
# Read the complete table
man.data <- read.table("C:/Users/sarlago/Documents/R scripts/Shiny/ShinyTest/data/GWAScatalog_KidneyDisease/26831199-GCST003374-EFO_0003884.h.tsv.gz", sep = "\t", header = T) 

# remove NAs
man.data <-  man.data[!is.na(man.data$hm_chrom),]
# paste chr to chr name
man.data$hm_chrom <- paste("chr", man.data$hm_chrom, sep="")
# select just the columns with the required info and write output to file
man.data %>% 
  relocate(chrom = "hm_chrom", pos = "hm_pos", p = "p_value", snp = "hm_rsid") %>% 
  write.table("C:/Users/sarlago/Documents/R scripts/Shiny/ShinyTest/data/GWAScatalog_KidneyDisease/26831199-GCST003374-EFO_0003884.h.relocatedCol.tsv.gz", sep="\t", col.names = T, row.names = F, quote = F)

unique(man.data$hm_chrom)
```




```{r sesionInfo, echo=FALSE}
sessionInfo()
```

