---
title: "GV_files_organization"
author: "Sara Lago"
date: "2026-07-31"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Genomic Viewer files organization

------------------------------------------------------------------------

## Table of Contents

<details open>
<summary>&nbsp;</summary>

1.  [Dev Version](#dev-version)
2.  [Docker Version](#docker-version)
3.  [Dev vs Docker app.R version](#dev-vs-docker)
4.  [GV Installer](#gv-installer)

</details>

------------------------------------------------------------------------

## Dev Version {#dev-version}

All the ***Genomic Viewer*** files used for development are in the 
[GenomicViewer_local](https://scientificnet-my.sharepoint.com/:f:/r/personal/sarlago_eurac_edu/Documents/Manuscripts/GenomicViewer_manuscript/GenomicViewer_local?csf=1&web=1&e=1abiIB) directory.

### Files description {#files-description-local}

The directory content is organized as follows:

#### Main GV functions:

- *GenomicViewer_app.R*: This is the Shiny code handling the ui and server 
                          functions of the application. It also loads necessary
                          R libraries and reads in the configuration file.
                          
- *plotgardener_function.R*: This is the function used to create the genomic 
                             view plots displayed in the *Plot* navigation tab.
                             
- *shiny_read_table_function.R*: This is the function to read raw data tables to
                                 be displayed in the *Data* navigation tab.
                                 
- *basic_statistics_genome_tracks_function.R*: This is the function to generate 
                                               basic statistics plots displayed 
                                               in the *Stats* navigation tab.

- *file_validation_function.r* Input file sanitization.

#### Configuration file:

- *GenomicViewer_config.yml*: Pre-filled configuration file with whole data used
                              in the tutorial (not subsetted to chr5).
                              
Note 1: change `data.dir` with your local directory with the corresponding data. 

Note 2: the keys `chrom.cen.dir` and `genes.hgnc.dir` are only required in the 
dev version as are handled in a separated configuration file that the user should 
not change in the docker version.


#### R environment files:

- *renv directory and renv.lock*: use these to restore the R environment with 
                                  the correct version of all packages through the
                                  command `renv::restore()`.
                                  
### Public web assets directory:

- *www directory*: contains the GV logo to be accessed and displayed in the html
                   version of the Shiny app.

#### Genome Annotations:

- *centromers directory*: Contains UCSC files with cytobands for all the GV 
                          available reference genomes, the R scripts used to 
                          retrieve the centromers, and resulting centromers and 
                          the resulting centromers files used to create the 
                          chromosome selection plot in GV app.

- *hgnc symbols directory*: Contains R scripts used to obtained organized lists 
                            of gene symbols used in the **Search by gene** menu 
                            of GV interface, as well as the resulting files.
                            
- *T2T_txdb*: custom R package to have the annotation information for T2T reference
              genome. This can be installed into R through 
              `devtools::install('/T2T_txdb/TxDb.Hsapiens.UCSC.T2T.knownGene/inst/extdata/')`
              
## Setting up GV files to work locally

Recommended file folder structure:

```
GenomicViewer_local
│
│   basic_statistics_genome_tracks_function.r
│   GenomicViewer_app.r
│   GenomicViewer_config.yml
│   plotgardener_function.r
│   renv.lock
│   shiny_read_table_function.R
│
├───centromers
│       chm13v2.0_cytobands_allchrs.bed
│       chrom_centromeres_hg19.txt
│       chrom_centromeres_hg38.txt
│       chrom_centromeres_mm10.txt
│       chrom_centromeres_mm39.txt
│       chrom_centromeres_T2T.txt
│       chrom_sizes_T2T.txt
│       cytoBand_GRCm39.txt
│       cytoBand_hg19.txt
│       cytoBand_mm10.txt
│
├───hgnc_symbols
│       hg19_gene_symbol_cleaned.bed
│       hg38_gene_symbol_cleaned.bed
│       mm10_gene_symbol_cleaned.bed
│       mm39_gene_symbol_cleaned.bed
│       T2T_gene_symbol_cleaned.bed
│
├───renv
│
├───T2T_txdb
│   └───TxDb.Hsapiens.UCSC.T2T.knownGene
│
└───www
        GV_logo.png
        
```


It follows the step by step instructions for setting up GV on your computer.

1. Download R version 4.4.3 and Bioconductor 3.20.

2. Restore all required R libraries through `renv`:
    - set working directory to the directory where you have `renv.lock` and `renv`
    files.
    
    - Run `renv::activate()` and `renv::restore` to install packages.
    
    - Manually install the remaining packages: 
    `install.packages('R.utils', repos = c(CRAN = 'https://cloud.r-project.org'))`
    `install.packages('devtools', repos = c(CRAN = 'https://cloud.r-project.org'))`
    
    - Install the T2T ref genome package:
    `devtools::install('T2T_txdb/TxDb.Hsapiens.UCSC.T2T.knownGene')`
    
3. Fill the configuration file with the data to be visualized. E.g. if you 
   download from [GitHub](https://github.com/EuracBiomedicalResearch/genomic_viewer/tree/docker-genomicviewer/GV_installer_electron/assets/example_data) 
   the `example data` directory, your configuration file
   `GenomicViewer_config.yml` should look like this:
   
```{yml, eval = F}

---

default:

    # Set here the parameters related to the input files path and fileensions
  # Data directory
  data.dir: "path/to/example_data/directory"
  # bigWig section
  bw.dir: "GSE212908_RAW_ATAC_bigwig"
  bw.file: "treat_pileup_chr5.bw"
  bw.names: ["Kidney cortex 12", "Kidney cortex 15"]
  # bedpe section
  bedpe.dir: "GSE212910_RAW_HiC_bedpe"
  bedpe.file: "GSM6560960_mustache_0.1_0.2_out.diffloops_in_cortex_2_chr5.bedpe"
  bedpe.names: ["HiC arches"]
  # bed section
  bed.dir: "GSE212908_ATAC_peaks"
  bed.file: "GSE212908_RAM012_013_015_peak_masterlist_chr5.bed"
  bed.names: ["ATAC peaks"]
  # hic section
  hic.dir: "GSE212910_RAW_HiC"
  hic.file: "GSM7749626_Cortex_partitioned_donor5_DM_chr5_50000.ginteractions.tsv.short.sorted.hic"
  hic.names: ["HiC cortex"]
  # GWAS section
  gwas.dir: "GWAScatalog_KidneyDisease"
  gwas.file: "relocatedCol_chr5.tsv"
  gwas.names: ["GWAS chronic kidney disease"]
  # categorical bed section
  cat.dir: ""
  cat.file: "regulatory_elements_hg38_chr5.bed"
  cat.names: ["Regulatory Elements"]
  
  # directory with chromosomes and centromeres coordinates. 
  # !! Write the entire path to the centromers directory if not in your R working directory !!
  chrom.cen.dir: "centromers"
  # directory with desired genome genes hgnc symbol and coordinates.
  # !! Write the entire path to the hgnc_symbols directory if not in your R working directory !!
  genes.hgnc.dir: "hgnc_symbols"

```

What you have to modify in the configuration file are your local paths to:

- `data.dir`

- `chrom.cen.dir`

- `genes.hgnc.dir`

4. Next you must ensure that the configuration file path is specified in the 
`GenomicViewer_app.r` file. To do so, open the `GenomicViewer_app.r` file in 
RStudio and specific your local path to the configuration file in the code chunk
starting at line 60

```{r, get_config, eval = F}

## Load config file and handle parsing errors like invalid YAML, bad indentation, missing ":".
config <- tryCatch(
  config::get(file = "local/path/to/your/GenomicViewer_config.yml"),
  error = function(e) {
    stop("#### CONFIGURATION ERROR #### \n GenomicViewer_config.yml: ", e$message, call. = FALSE)
  }
)
```

              
5. You are now ready to run the application. From the `GenomicViewer_app.r` file 
in RStudio click the `Run App` button in the top right corner.


## Docker Version {#docker-version}

The source code of ***Genomic Viewer*** application for Docker is available 
through [GitHub](https://github.com/EuracBiomedicalResearch/genomic_viewer).

--------------------------------------------------------------------------------

## Docker files:

In the following section you will find the instruction for setting up GV Docker
container.

### Files description Docker

- *Dockerfile*: handles the setting up of the Docker environment. Takes care of 
                installing the docker base image with shiny and the required OS 
                libraries, restores the correct R environment, installs T2T 
                genome annotation package, copies all GV files in the correct 
                position of the Docker container, exposes the 8180 port and runs 
                the app.
                
  Note: to update the latest GV docker build use `docker build -t sarlago/shiny-docker-genomicviewer2 .`
  To publish the updated version `docker push sarlago/shiny-docker-genomicviewer2`.
  
- *Docker_files directory*: contains all the files rquired for the app to work 
                            as listed for [Dev version](#file-description-local).
                            
Note: In this version there is an additional configuration file for the genome 
annotation files which should not be modified by users for safety. 
This is `GenomicViewer_config_gen.yml` file. The keys that are specified in this 
file are absent in the Docker version of the `GenomicViewer_config.yml` file.

- *data directory*: contains the example data used in the tutorial.

## Setting up GV files for Docker

Recommended file folder structure:

```
GenomicViewer
│   Dockerfile
│
└───Docker_files
    │     .Rprofile
    │     basic_statistics_genome_tracks_function.r
    │     GenomicViewer_app.r
    │     GenomicViewer_config_gen.yml
    │     plotgardener_function.r
    │     renv.lock
    │     shiny_read_table_function.R
    │
    ├───centromers
    │       chm13v2.0_cytobands_allchrs.bed
    │       chrom_centromeres_hg19.txt
    │       chrom_centromeres_hg38.txt
    │       chrom_centromeres_mm10.txt
    │       chrom_centromeres_mm39.txt
    │       chrom_centromeres_T2T.txt
    │       chrom_sizes_T2T.txt
    │       cytoBand_GRCm39.txt
    │       cytoBand_hg19.txt
    │       cytoBand_mm10.txt
    │
    ├───hgnc_symbols
    │       hg19_gene_symbol_cleaned.bed
    │       hg38_gene_symbol_cleaned.bed
    │       mm10_gene_symbol_cleaned.bed
    │       mm39_gene_symbol_cleaned.bed
    │       T2T_gene_symbol_cleaned.bed
    │
    ├───renv
    │
    ├───T2T_txdb
    │   └───TxDb.Hsapiens.UCSC.T2T.knownGene
    │
    └───www
            GV_logo.png
        
```

After setting the correct folders/files tree, to create the Docker container you must:

1. Activate docker engine.

2. Open a Terminal in the `GenomicViewer` directory containing the `Dockerfiles`.

3. Build the container through `docker build -t docker_usrname/container_name .`.

4. Publish the container to Docker Hub through `docker push docker_usrname/container_name`.
   This will automatically be assigned to the `latest` tag and overwrite the
   previous published version unless you do not specify a different tag.
   
   At the moment GV is published in Docker Hub as `sarlago/shiny-docker-genomicviewer2`.

-------------------------------------------------------------------------------

## Dev vs Docker app.R {#dev-vs-docker}

The `GenomicViewer_app.r` contains Shiny logic to make the application work. The
Dev and Docker versions have few but key differences since they run through 
different execution environments. In addition there are some differences motivated
by practical reasons.

All relevant differences (excluding white spaces, tabs, newlines or debug comments)
are explained below:

**1. Loading Genome annotation config file**

As mentioned above, the Docker version needs an additional configuration file
with genomic annotation source files.

Lines 51-52 of Docker version:

```{r, eval = F}

## Load config_gen file with genome annotations, not modifiable by the user.
config_gen <- config::get(file = "GenomicViewer_config_gen.yml")

```

This option is absent in the Dev version since genome annotation files are 
directly imported through the main configuration file.


**2. Loading the main config file**

In the Docker version the `GenomicViewer_config.yml` file is always searched in
 `/data/GenomicViewer_config.yml`.
 
Lines 56 of Docker version:

```{r, eval = F}

  config::get(file = "/data/GenomicViewer_config.yml"),

```

In the Dev version the user can manually specifiy a different configuration file
path and name.

Line 59 of Dev version:

```{r, eval = F}

  config::get(file = "GenomicViewer_config.yml"),

```


**3. Reading data from config file**

In the Docker version the data that the user choose to visualize are saved in a
`/data` folder that is mounted a volume by Docker upon installation. This is the
only way Docker can access your local data. In Docker `/data` becomes an absolute
directory inside the container root, thus you need to start with a backslash to
prevent Shiny to search for files from the default Shiny-server directory inside
Docker, typically `/srv/shiny-server/`.

Thus when using `file.path()` to access file names, a heading backslash is specified.
Lines 141-153 in Docker version:

```{r, eval = F}

# Set a BigWig file
bw.file <- unlist(lapply(config$bw.file, function(p) dir(file.path("/", config$data.dir, config$bw.dir), recursive = T, include.dirs = T, full.names = TRUE, pattern = p)))
# Set a bed file
bedpe.file <- unlist(lapply(config$bedpe.file, function(p) dir(file.path("/", config$data.dir, config$bedpe.dir), recursive = T, include.dirs = T, full.names = TRUE, pattern = p)))
# Set a bedpe file
bed.file <- unlist(lapply(config$bed.file, function(p) dir(file.path("/", config$data.dir, config$bed.dir), recursive = T, include.dirs = T, full.names = TRUE, pattern = p)))
# Set hiC data file
hic.file <- unlist(lapply(config$hic.file, function(p) dir(file.path("/", config$data.dir, config$hic.dir), recursive = T, include.dirs = T, full.names = TRUE, pattern = p)))
# Set GWAS data file
gwas.file <- unlist(lapply(config$gwas.file, function(p) dir(file.path("/", config$data.dir, config$gwas.dir), recursive = T, include.dirs = T, full.names = TRUE, pattern = p)))
# Categorical bed file
cat.file <- unlist(lapply(config$cat.file, function(p) dir(file.path("/", config$data.dir, config$cat.dir), recursive = T, include.dirs = T, full.names = TRUE, pattern = p)))
# Region Table file
saved.coord.path <- dir(file.path("/", config$data.dir, config$reg.dir), recursive = T, include.dirs = T, full.names = TRUE, pattern = config$reg.file)

```

**4. Static Resources for browser**

When adding static resoures to your Shiny app, it automatically exposes a 
directory called `www`. In our case it contains GV logo.
Docker container does not automatically expose this directory because it is not
in the default shiny server, but is in the app directory we created in the 
contaire, therefore we need to expose the `www` directory manually in the Docker
version.

Lin 162 of Docker version:

```{r, eval = F}

shiny::addResourcePath('www', '/shiny-app-GenomicViewer/www')

```

This also affects line 177 of Docker version where we need to recall the logo 
path for displaying in the browser:

```{r, eval = F}

span("", img(src = "www/GV_logo.png", height = 50, style = "margin-left:14%; margin-top:-50px" )),

```

(`www` does not need to be specified in the Dev version)


**5. Defining reactive events for reference genome related files**

In the Shiny server logic file with reference genomes annotations are read
dynamically from the genomic annotations files provided through the main
`GenomicViewer_config.yml` file in the Dev version or through the 
`GenomicViewer_config_gen.yml` file in the Docker version.

This implies differences in how the file paths are called at lines 405, 411, 428 
and 432 of the Docker version file:

```{r, eval = F}
  # Genes hgnc symbol l. 405
  genes.hgnc.path <- file.path(config_gen$genes.hgnc.dir, paste(gsub( " .*", "", input$ref.genome), "_gene_symbol_cleaned.bed", sep=""))

  ### For chromosomes plotting l. 411
  chrom.cen.path <- file.path(config_gen$chrom.cen.dir, paste("chrom_centromeres_", gsub( " .*", "", input$ref.genome), ".txt", sep=""))
  
  ### For cytoband l. 428
  cytoband <- read_delim(file.path(config_gen$chrom.cen.dir, "chm13v2.0_cytobands_allchrs.bed"), delim = "\t", col_names = F)
  
  # l. 432
  cytoband <- read_delim(file.path(config_gen$chrom.cen.dir, "cytoBand_GRCm39.txt"), delim = "\t", col_names = F)

```

`config_gen` variable is used instead of `config`.


**6. Stop Shiny app process when user closes the browser**

In the Docjer version, when user closes browser the app process stops automatically
thanks to the command at line 1614:

```{r, eval = F}

    session$onSessionEnded(function() { stopApp() })

```

This option has not been added in the Dev version to have greater control.

-------------------------------------------------------------------------------

## GV Installer {#gv-installer}

The GV Installer has been created using Electron framework. All the necessary 
files are in the *GV_Installer_electron* directory on 
[GitHub](https://github.com/EuracBiomedicalResearch/genomic_viewer). 

### Installer Files Description

The required files to create an Electron based installer are the following:

- *main.js*: creates the installer window, loads `index.html` and handles all the
  installer events communicating with the `render,js` file. (backend)
  
- *renderer.js*: renders process logic, handles buttons and user messages, udating
  dynamically the UI. (frontend)
  
- *preload.js*: secure bridge between main and renderer.

- *index.html*: this defines the user interface defining the actual window content 
   and structure.
   
- *package.json*: this is used for installer configuration, defining metadata and
  dependencies.
  
- *package-lock.json*: defines dependencies to ensure consistent builds, this is
  generated automatically by Electron.
  
- *forge.config.json*: Electron Forge configuration that controls packaging and 
  distribution behavior defining makers for the different OSs, plugins, icons and
  other building configurations.
  
- *assets directory*: stores additional files that are handled by the installer
  as external resources, like icons, example data files, runner scripts to launch 
  GV and the create-desktop-shortcut package which was otherwise not accessible
  from within Electron and the `GenomicViewer_config.yml` file.
  
Recommended files tree:

```
GV_installer_electron
│       forge.config.js
│       index.html
│       main.js
│       package-lock.json
│       package.json
│       preload.js
│       renderer.js
│
├───assets
│   │ 	GenomicViewer_config.yml
│   │ 	GenomicViewer_linux.sh
│   │ 	GenomicViewer_mac.sh
│   │	  GenomicViewer_win.bat
│   │	  GV_icon.icns
│   │	  GV_icon.ico
│   │	  GV_icon.png
│   │	  GV_installer_logo.png
│   │	  
│   ├───create-desktop-shortcuts
│   │   
│   └───example_data
│
└───node_modules (only for local build, not GitHub Actions)     

```

### Local build of the installer

You need to install `npm`, this automatically creates the node_modules directory 
that contains the actual code for Electron. All the specified dependencies are 
imported form here.

To setup the `node_modules` run `npm install` from within the directory containing
*package.json* and *package-lock.json*.

Once the correct file tree is setup and `npm` with `node_modules` installed you
can run the installer app for testing opening a terminal in the directory with
electron files through:

`npm run start`

Or you can package the app to be distributed through:

`npm run make`

Note: Local build of the distributable app package is only possible for your 
working OS. 
To build a cross-platform Electron app one solution is to use GitHub Actions.

### Cross-platform building of the installer

To build the installer in a cross-platform way through GitHub Actions you can
commit to GitHub the requires files tree as reported above. Inside 
`Electron_GV_installer` parent directory create `.github/workflows/build.yml`
which os used to rebuild the installer distributable package after any push.

Tip: comment out the content of `on:` key to prevent unwanted rebuild before 
pushing commits.

The GitHub build workflow code should look like this:


```{yml, eval = F}

name: Build and Publish GenomicViewer installer Electron App

on:
  push:
    branches: [ docker-genomicviewer]
  pull_request:
    branches: [ docker-genomicviewer ]
  workflow_dispatch:

permissions:
  contents: write

jobs:
  build-linux:
    runs-on: ubuntu-latest
    steps:
      - uses: actions/checkout@v3
      - uses: actions/setup-node@v3
        with:
          node-version: 18
          cache: 'npm'
  
      - run: npm install
      - run: npx electron-forge make --platform=linux --arch=x64
      - run: ls -lR out/make/

      - uses: actions/upload-artifact@v4
        with:
          name: linux-x64
          path: out/make/

  build-windows:
    runs-on: windows-latest
    steps:
      - uses: actions/checkout@v3

      - uses: actions/setup-node@v3
        with:
          node-version: 18
          cache: 'npm'

      - run: npm install
      - run: npx electron-forge make --platform=win32 --arch=x64

      - uses: actions/upload-artifact@v4
        with:
          name: windows-x64
          path: out/make/

  build-macos-arm64:
    runs-on: macos-latest  # Apple Silicon
    steps:
      - uses: actions/checkout@v3

      - uses: actions/setup-node@v3
        with:
          node-version: 18
          cache: 'npm'

      - run: npm install
      - run: npx electron-forge make --platform=darwin --arch=arm64

      - uses: actions/upload-artifact@v4
        with:
          name: macos-arm64
          path: out/make/

  publish:
    needs: [build-linux, build-windows, build-macos-arm64]
    runs-on: ubuntu-latest
    if: startsWith(github.ref, 'refs/tags/')
    steps:
      - uses: actions/download-artifact@v4
        with:
          path: ./dist

      - run: npm ci
      - run: npm run publish
        env:
          GITHUB_TOKEN: ${{ secrets.GITHUB_TOKEN }}
```


### MacOS Installer

Despite GitHub Actions allows to build the GV Installer app for macOS, modern
macOS releases prevent it to run without a licence. We solved this issue by 
using a simple launcher script in place of the ELectron Installer. The script is
available through [GitHub](https://github.com/EuracBiomedicalResearch/genomic_viewer/tree/docker-genomicviewer/Installer_Mac)
and its usage is described in the [GV README](https://github.com/EuracBiomedicalResearch/genomic_viewer?tab=readme-ov-file#macos).

### Self-contained AppImage building for non-root Linux users

To build the non-root user AppImage for GV use 
[*appimagetool*](https://github.com/AppImage/appimagetool/releases/tag/continuous)
starting from the .deb GV package created either locally from a Linux pc or through
GitHub Actions. The .deb package will already contain all the necessary files.

Below are the detailed instructions to build the GV AppImage:

1. **Install appimagetool** 

  Download the official binary from 
  [GitHub release](https://github.com/AppImage/appimagetool/releases/tag/continuous).
  
  Make it executable `chmod +x appimagetool-x86_64.AppImage`.
  
2. **Extract your GV app .deb package**

  Assuming your .deb file is `genomicviewer-gui-installer_1.0.0_amd64.deb`.
  Extract it to a directory e.g. 
  
  
```{sh, eval = F}

  mkdir deb-extract
  dpkg-deb -x genomicviewer-gui-installer_1.0.0_amd64.deb deb-extract

```
  
3. **Create AppDir structure**

Create the AppDir folder first and move there the content of deb-extract:
    
```{sh, eval = F}

mkdir -p GV.AppDir
mv deb-extract/* GV.AppDir

```
    
4. **Create an AppRun launcher file**

Inside GV.AppDir/ create an AppRun file with the following content:

```{bash, eval = F}

#!/bin/bash
DIR="$(dirname "$(readlink -f "$0")")" 
 
export PATH="$DIR/usr/bin:$PATH" 
export LD_LIBRARY_PATH="$DIR/usr/lib:$LD_LIBRARY_PATH"
 
# Execute the main application
"$DIR/usr/bin/genomicviewer-gui-installer" "$@"

```


Make it executable:

```{sh, eval = F}

chmod +x GV.AppDir/AppRun

```


5. **Copy the .desktop file**

Copy the `.desktop` file from the `.deb` into the GV.AppDir root

```{sh, eval = F}

cp GV.AppDir/usr/share/applications/*.desktop GV.AppDir/genomicviewer-gui-installer.desktop

```


Then edit it so that its content is like follows:

```
[Desktop Entry]
Name=genomicviewer-gui-installer
Comment=Shiny based app for the visualization and basic analysis of NGS data.
GenericName=genomicviewer-gui-installer
Exec=genomicviewer-gui-installer
Icon=genomicviewer-gui-installer
Type=Application
Categories=GNOME;GTK;Utility;

```

6. **Copy the GV icon**

The GV icon that is inside the originally extracted .deb package must be copied 
in the GV.AppDir root

```{sh, eval = F}

cp GV.AppDir/usr/share/icons/pixmaps/genomicviewer-gui-installer.png \
   GV.AppDir/genomicviewer-gui-installer.png


```


7. **Build AppImage using appimagetool**

To build the self-contained AppImage using the downloaded binaries for appimagetool
run the following command from the GV.AppDir parent directory:

```{sh, eval = F}

ARCH=x86_64 /home/user/Appimagetool/appimagetool-x86_64.AppImage GV.AppDir

```

This produces:

`genomicviewer-gui-installes-x86_64.AppImage`

Which is your selft-contained distributable GenomicViewer AppImage for Linux.

You can run the image as follows:

```{sh, eval = F}
# make it executable
chmod +x genomicviewer-gui-installer-x86_64.AppImage

# run the app without root privileges
./genomicviewer-gui-installer-x86_64.AppImage --no-sandbox

```

Note: the `--no-sandbox` option was required to me since working on an Ubuntu VM,
might not be required in your case.


