---
title: "hg19_centromers"
author: "Sara Lago"
date: "2025-04-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##### GENERATING hg19 CENTROMERS COORDINATES FILE ######

The coordinates for hg19 centromere bands were downloaded from https://github.com/marbl/CHM13?tab=readme-ov-file
The file contains several bins corresponding to the centromere for every chromosome.
The chrom sizes for T2>T genome are still not available through the Txdb package tehrefore they were downloaded from https://hgdownload.soe.ucsc.edu/goldenPath/hs1/bigZips/
Here we will generate a table with:
  - centromere start and end positions;
  - the corresponding chromosome start and end positions. 
  
  ###### 1) LIBRARIES ######
```{r readlibraries, warning=F, message=F}

library(dplyr)
library(data.table)
library(ggplot2)
library(ggchicklet)

```
  
  
  ###### 2) READ THE UCSC FILE ######
```{r readfile, warning=F, message=F, echo=F}

centromere.fileread <- read.table("chm13v2.0_cytobands_allchrs.bed", header = F, sep="\t")
colnames(centromere.fileread) <- c("chr", "start", "end", "id", "band")

# Filter the banding corresponding to the centromere, called acen
centromere.fileread <- dplyr::filter(centromere.fileread, band == "acen")

# read the chrom sizes file
chromSizes <- read.table("chrom_sizes_T2T.txt", header = F, sep ="\t")
colnames(chromSizes) <- c("chr", "chr.len")

```

  ###### 3) PROCESS THE FILE ######
```{r calculate start end, warning=F, message=F, echo=F}
# Calculate for every chromosome the min and max coordinate
min <- c()
max <- c()

for (i in unique(centromere.fileread$chr)){
  chr.sel <- filter(centromere.fileread, chr == i)
  min <- c(min, min(chr.sel$start))
  max <- c(max, max(chr.sel$end))
}

  # Save results in a data frame
chr.coord.df <- data.frame(chr = unique(centromere.fileread$chr),
                           cen.start = min,
                           cen.end = max)

```
  
  ###### 4) GET CHROMOSOME SIZES AND ADD INFO TO CENTROMERE TABLE ######
```{r chr.size, message=F, warning=F}

## Merge chrom sizes with centromeres table
chrom.cen.df <- merge(x = chr.coord.df, y = chromSizes, by = "chr")

## Sort so that chromosomes are in the correct order
chrom.cen.df <- arrange(chrom.cen.df, suppressWarnings(readr::parse_number(chr)))
## Add order row
chrom.cen.df$order <- c(1:24)
```

  ###### 5) EXPORT TABLE ######
```{r exp.table, warning=F, message=F}
## Export the table with chrom sizes and centromers coordinates to file
write.table(chrom.cen.df, "chrom_centromeres_T2T.txt", row.names = F, col.names = T, quote = F, sep="\t")

```
  
  ###### 6) GENERATE A PLOT RESEMBLING CHROMOSOMES WITH CENTROMERES USING GGPLOT ######
```{r chrom.plot, message=F, warning=F}
ggplot(chrom.cen.df) +
  ggchicklet:::geom_rrect(aes(xmin = order - 0.25,
                              xmax = order + 0.25,
                              ymin = cen.start,
                              ymax = chr.len,
                              fill = chr)) +
  ggchicklet:::geom_rrect(aes(xmin = order - 0.25,
                              xmax = order + 0.25,
                              ymin = 0,
                              ymax = cen.end,
                              fill = chr)) +
  scale_x_continuous(breaks = c(1:24), labels = factor(chrom.cen.df$chr, levels = chrom.cen.df$chr)) +
  theme_void() +
  theme(legend.position = "none",
        axis.ticks.x = element_line(size = 2, linetype = 2),
        axis.text.x = element_text(angle = 90, face = "bold")) 
```

  
  
  